---
title: "Data analysis(Nina)"
format: html
editor: visual
---

## Data Analysis and Results

**3.1 Data Pre-processing**

Data was examined before our modeling, including checking for missing values and removing outliers.

\[From Arun code and content\]

**3.2 Data Distribution**

Ggplot was utilized to show how many RSV cases and how many percent positive cases was detected in CDC participating laboratories weekly since Nov 14, 2020.

In the first graph below shows RSV cases weekly trend. Each dot represent one weekly PCR Detection number. It looks like the dots form a curve line with a peek in the end of 2021 and constantly rising at the end. It is not a linear distribution.

```{r}
library(readxl)
# data <- read_excel("C:/Data science courses/STA6257/Research project/RSV Data for the US.xlsx")
# View(RSV_Data_for_the_US)
library(tidyverse)
data <- read_excel("/Users/arunraj/Documents/MS Data Science/Advance Statistical Modeling/Week1-Project/PolynomialRegressionArNa/NinaCode/RSVProject/RSVproject2022/RSV Data for the US.xlsx")
ggplot(data=data,aes(x=RepWeekDate,y=PCRDetectionsNumerator))+geom_point()

```

The graph below with the percent of the positive cases in weekly PCR detection also show a similar curve line. While, it has a greater rise in the end of 2021.

```{r}
ggplot(data=data,aes(x=RepWeekDate,y=PCRDetectionPercent))+geom_point()

```

**3.3 Polynomial Regression Model Analysis**

Data was split into train data and test data, and a comparision was made to decide which degree of model is the best fit.

| Degree | Multiple R-square | MSE (error) |
|--------|-------------------|-------------|
| 1      | 0.2143            | 2198        |
| 2      | 0.2144            | 2201        |
| 3      | 0.4382            | 1719        |
| 4      | 0.8054            | 802         |
| 5      | 0.8083            | 781         |
| 6      | 0.8156            | 752         |
| 7      | 0.8441            | 701         |
| 8      | 0.855             | 670         |
| 9      | 0.8713            | 623         |
| 10     | 0.9004            | 503         |
|        |                   |             |

```{r}
install.packages("caret")
install.packages("caTools")
```

```{r}
library(caret)
library(caTools)
my_data<-data
#split data into training and test
set.seed(150)
training.samples <-data$PCRDetectionsNumerator %>%
  createDataPartition(p=0.8,list=FALSE)
train.data<-my_data[training.samples, ]
test.data<-my_data[-training.samples, ]
#build model
model<-lm(PCRDetectionsNumerator~poly(Week,4,raw=TRUE),data=train.data)
summary(model)
#predict using the model
predictions<-model %>% predict(test.data)
compare <-data.frame(actual=test.data$PCRDetectionsNumerator,predicted=predictions)
#error
error<-RMSE(predictions,test.data$PCRDetectionsNumerator)
```

Degree of 4 was selected based on relatively higher multiple r-square and lower error. Even through degree of 5 and up slightly increased the multiple r-square and decreased the lower error, it will overfit the training set and will be a poor fit for the cross validation set.

**3.4 Model performance**

P-value for each polynomial degree is less than 0.05 through t-test. There is significant evidence to reject the H0 and a model of PCRDetectionNumerator = 1450-429Week+26Week^2^ -0.46Week^3^ -0.0024Week^4^ is suggested.

```{r}
summary(model)
```

The line in the graph is generated based on our model. It is a good fit to predict the positive cases of Respiratory syncytial virus.

```{r}
# model performance
modelPerformance=data.frame(RMSE=RMSE(predictions,test.data$PCRDetectionsNumerator),R2=R2(predictions,test.data$PCRDetectionsNumerator))
ggplot(train.data,aes(Week,PCRDetectionsNumerator))+geom_point()+stat_smooth(method=lm,formula=y~poly(x,4,raw=TRUE))
```
